---
title: "Errata"
subtitle: "On Coppock and McClellan (2019), *Research and Politics* 6(1)"
format:
  pdf:
    output-file: coppock_mcclellan_2019_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
here::i_am("errata.qmd")

out <- function(f) read_csv(here("maintained", "output", f), show_col_types = FALSE)

distances <- out("appendix_table_1_distance_tests.csv")
counts <- out("appendix_table_1_distance_counts.csv")
demos <- out("table_1_demographics.csv")
fig1 <- out("figure_1_standardized_demos.csv")
welfare_ns <- out("table_4_welfare_ns.csv")
kamsimas <- out("table_6_kamsimas.csv")
hiscox <- out("table_7_hiscox.csv")

# The string the article prints, kept as a string: a type guess turns 0.100 into 0.1 and
# destroys the precision the page carries.
published <- read_csv(here("ground_truth", "published_claims.csv"),
                      col_types = cols(.default = col_character()))

# Every number in a corrected sentence below is computed here, at the time this document
# is rendered, from the deposited data. That includes the numbers that were not wrong: a
# token carried over from the published sentence is inherited on trust, and rendering the
# whole sentence from the pipeline is what verifies it.
cell <- function(tab, var, col) {
  value <- tab[[col]][tab$variable == var]
  stopifnot(length(value) == 1)
  as.numeric(str_remove_all(str_extract(value, "^[$]?-?[0-9,.]+"), "[$,]"))
}

standardized <- function(var, survey_id) {
  value <- fig1$mean[fig1$variable == var & fig1$survey == survey_id]
  stopifnot(length(value) == 1)
  value
}

dist_row <- function(var) {
  row <- distances[distances$variable == var, ]
  stopifnot(nrow(row) == 1)
  row
}

# The article's own cell, quoted rather than retyped.
page <- function(id) {
  value <- published$value_paper[published$claim_id == id]
  stopifnot(length(value) == 1)
  value
}

fitted_n <- function(tab, key, value) {
  n <- unique(tab$nobs[tab[[key]] == value])
  stopifnot(length(n) == 1)
  n
}

# Recomputed from the distance and standard error appendix Table 1 itself prints, so this
# arithmetic does not depend on rerunning the deposit's unseeded bootstrap.
published_a1 <- published |>
  filter(str_starts(claim_id, "a1_")) |>
  transmute(quantity = str_extract(claim_id, "(?<=^a1_)[a-z]+"),
            variable = str_remove(claim_id, "^a1_[a-z]+_"),
            value = as.numeric(value_paper)) |>
  pivot_wider(names_from = quantity, values_from = value) |>
  mutate(z = distance / se, p_twotail = 2 * pnorm(-abs(z)))

page_z <- function(var) published_a1$z[published_a1$variable == var]
page_p_twotail <- function(var) published_a1$p_twotail[published_a1$variable == var]

trait_vars <- c("extraversion", "agreeableness", "conscientiousness",
                "emotionalstability", "opennesstoexperiences")
trait_rows <- filter(distances, variable %in% trait_vars)
traits_significant <- sum(trait_rows$lucid_is_closer > 0 & trait_rows$p_twotail < 0.05)

demographic_vars <- c("female", "education", "age", "income", "race_white", "race_black",
                      "race_hispanic", "region_northeast", "region_midwest",
                      "region_south", "region_west")
demographic_rows <- filter(distances, variable %in% demographic_vars)
demographic_closer <- sum(demographic_rows$lucid_is_closer > 0)
demographic_significant <- sum(demographic_rows$lucid_is_closer > 0 &
                                 demographic_rows$p_archive < 0.05)
demographic_names <- demographic_rows$varname[demographic_rows$lucid_is_closer > 0 &
                                                demographic_rows$p_archive < 0.05]

# A corrected count that the article spelled out has to come back as a word.
words <- c("zero", "one", "two", "three", "four", "five", "six", "seven", "eight",
           "nine", "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen",
           "sixteen", "seventeen", "eighteen", "nineteen", "twenty")
word <- function(n) words[[n + 1]]

# One decimal on the percentage point scale throughout, and thousands separators on a
# sample size, matching the appendix's own typography.
pts <- function(x) str_replace(sprintf("%.1f", x), "^-", "\u2013")
sd_fmt <- function(x) str_replace(sprintf("%.3f", x), "^-", "\u2013")
n_fmt <- function(x) format(x, big.mark = ",", trim = TRUE)

# The appendix prints its p-values to three decimals, so a corrected p-value does too.
p_fmt <- function(x) sprintf("%.3f", x)
```

```{r entries}
# THE ERRATA SPINE. Every entry is defined once, here, and rendered from here: into this
# document, and into whatever else needs it, which reads the errata_entries.csv written at
# the bottom of this file rather than keeping a second hand-typed copy.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here, \was{} in an edition. Nothing else in a field is markup, so the same string can be
# set by either. Every unmarked number in a corrected sentence is computed too, so a reader
# diffing published against corrected sees the whole sentence verified.
#
# Numbering is the published note's and is APPEND-ONLY: an entry can already have been
# cited, so a later finding is added at the end and never interleaved.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note,

  1, "quantity", "pipeline", "full",
  "Lucid is not significantly closer than MTurk on all five personality traits",
  "published, online appendix section 1",
  "Formal hypothesis tests demonstrate that Lucid is significantly closer to the ANES 2012 than MTurk on [[all five traits]].",
  str_glue("Formal hypothesis tests demonstrate that Lucid is significantly closer to the ANES 2012 than MTurk on [[{word(traits_significant)} of the five traits, extraversion excepted]]."),
  str_glue(
    "Appendix Table 1 prints {page('a1_distance_extraversion')} and ",
    "{page('a1_se_extraversion')} for extraversion's distance and bootstrapped standard ",
    "error. Those two numbers give `z` = {sprintf('%.2f', page_z('extraversion'))} and a ",
    "two-tailed p-value of {p_fmt(page_p_twotail('extraversion'))}, above the 0.05 ",
    "threshold; the table's own p-value column prints {page('a1_p_extraversion')}, which is ",
    "the deposit's expression rather than the two-tailed test. The maintained rewrite's ",
    "seeded run reaches the same conclusion, at `z` = ",
    "{sprintf('%.2f', dist_row('extraversion')$z)} and p = ",
    "{p_fmt(dist_row('extraversion')$p_twotail)}. The other four traits clear 0.05 by a ",
    "wide margin under either test."),

  2, "quantity", "pipeline", "full",
  "The number of significant differences in the online appendix",
  "published, online appendix section 1",
  "Out of 21 opportunities, Lucid is closer to the ANES 18 times, [[14]] of which are significant.",
  str_glue("Out of {counts$n_variables} opportunities, Lucid is closer to the ANES {counts$n_lucid_closer} times, [[{counts$n_sig_closer_twotail}]] of which are significant."),
  str_glue(
    "Extraversion is the difference between the two counts, for the reason given above. ",
    "Recomputing every p-value from the distance and standard error appendix Table 1 prints ",
    "gives the same {counts$n_sig_closer_twotail}. The sentence that follows it is ",
    "unaffected: MTurk is closer in {counts$n_mturk_closer} instances and significant in ",
    "{word(counts$n_sig_farther_twotail)}, voter turnout, under both tests."),

  3, "description", "pipeline", "full",
  "The MTurk sample under-represents southerners",
  "published, main text",
  "The regional balance on Lucid comes very close to the 2012 ANES, whereas the MTurk sample appears to [[overrepresent]] southerners.",
  "The regional balance on Lucid comes very close to the 2012 ANES, whereas the MTurk sample appears to [[underrepresent]] southerners.",
  str_glue(
    "The southern share is {pts(cell(demos, 'region_south', 'mturk'))} per cent on MTurk ",
    "against the ANES 2012 benchmark of {pts(cell(demos, 'region_south', 'anes2012'))}, so ",
    "MTurk sits ",
    "{pts(abs(cell(demos, 'region_south', 'mturk') - cell(demos, 'region_south', 'anes2012')))} ",
    "points below it; Lucid is at {pts(cell(demos, 'region_south', 'lucid'))}. Figure 1, ",
    "which is where the sentence sends the reader, plots the same thing in standard ",
    "deviations: MTurk at {sd_fmt(standardized('region_south', 'mturk'))} and Lucid at ",
    "{sd_fmt(standardized('region_south', 'lucid'))}, with the benchmark at zero. MTurk ",
    "over-represents the Northeast and the Midwest instead. Appendix Table 1 is unaffected: ",
    "it reports the distance between the two samples rather than the direction of either, ",
    "and its South row is right."),

  4, "quantity", "pipeline", "full",
  "Six demographic differences are significant, not five",
  "published, main text",
  "Out of the 11 demographic variables that are measured for both Lucid and MTurk, the Lucid mean is closer to the ANES mean in nine instances, [[five]] of which are statistically significant.",
  str_glue("Out of the {nrow(demographic_rows)} demographic variables that are measured for both Lucid and MTurk, the Lucid mean is closer to the ANES mean in {word(demographic_closer)} instances, [[{word(demographic_significant)}]] of which are statistically significant."),
  str_glue(
    "Appendix Table 1 prints a p-value below 0.05 for ",
    "{str_c(str_c(head(demographic_names, -1), collapse = ', '), ' and ', tail(demographic_names, 1))}, ",
    "and Lucid is the closer sample on all {word(demographic_significant)}. The count is the ",
    "same under the two-tailed test corrected in the first two entries, so it does not turn ",
    "on which p-value is used."),

  5, "quantity", "pipeline", "brief",
  "The sample size of the Lucid welfare replication",
  "published, online appendix section 2.1.3",
  "Sample: [[1,811]] Lucid respondents. [Online appendix, section 2.1.3]",
  str_glue("Sample: [[{n_fmt(welfare_ns$n[welfare_ns$survey == 'lucid'])}]] Lucid respondents."),
  str_glue(
    "{n_fmt(fitted_n(hiscox, 'survey', 'lucid'))} is the Lucid sample of the Hiscox ",
    "free-trade replication, reported in section 2.4.2 of the same appendix. The welfare ",
    "data hold {n_fmt(welfare_ns$rows[welfare_ns$survey == 'lucid'])} Lucid rows, of which ",
    "{n_fmt(welfare_ns$n[welfare_ns$survey == 'lucid'])} have a usable outcome, and the ",
    "manifest reports the analysed sample in every other section."),

  6, "quantity", "pipeline", "brief",
  "The sample size of the original Kam and Simas study",
  "published, online appendix section 2.3.1",
  "Sample: [[761]] respondents gathered from a Knowledge Networks national probability sample. [Online appendix, section 2.3.1]",
  str_glue("Sample: [[{n_fmt(fitted_n(kamsimas, 'model', 'kam_base'))}]] respondents gathered from a Knowledge Networks national probability sample."),
  str_glue(
    "Appendix Table 2 reports N = {n_fmt(fitted_n(kamsimas, 'model', 'kam_base'))} for all ",
    "three models fitted to this sample, and {n_fmt(fitted_n(kamsimas, 'model', 'kam_base'))} ",
    "is what the deposited data give. The manifest reports the analysed sample rather than ",
    "the source study's throughout: its entry for the 1984 General Social Survey gives ",
    "{n_fmt(welfare_ns$n[welfare_ns$survey == 'GSS84'])}, where the deposited file holds ",
    "{n_fmt(welfare_ns$rows[welfare_ns$survey == 'GSS84'])} respondents for that survey.")
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# The spine's markup, resolved for this document. Another renderer resolves it differently.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")

# A heading is only a heading when a blank line precedes it, which is why every emitted
# entry opens with one.
emit <- function(n) {
  e <- entries |> filter(entry == n)
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n> ", bold(e$published),
      "\n\nCorrected:\n\n> ", bold(e$corrected), "\n\n", e$note, "\n", sep = "")
}
```

This note lists `r word(nrow(entries))` corrections to "Validating the demographic, political, psychological, and experimental results obtained from a new source of online survey respondents," published in *Research and Politics* 6(1), doi [10.1177/2053168018822174](https://doi.org/10.1177/2053168018822174). **None of them changes a conclusion of the paper.** Two are counts of statistically significant differences that follow from the hypothesis test the appendix says it used rather than the one its code performs, one reverses the direction of a descriptive comparison, one is a count off by one, and two are sample sizes in the appendix study manifest. The paper's finding, that Lucid respondents track US national benchmarks well and can serve as a drop-in replacement for Mechanical Turk, is unaffected, as is its one negative result on the healthcare rumor corrections.

Every number in a corrected sentence below is computed from the deposited replication archive ([10.7910/DVN/DDWWJW](https://doi.org/10.7910/DVN/DDWWJW)) at the time this document is rendered, including the numbers that were not wrong. Bold marks the corrections. The code and output supporting each correction are at [github.com/active-maintenance-aec/coppock_mcclellan_2019](https://github.com/active-maintenance-aec/coppock_mcclellan_2019).

The first two entries share a cause. Section 1 of the online appendix states that "we obtain two-tailed p-values under a normal approximation," and the deposited `12_DistanceTests.R` instead computes `pnorm(2 * (1 - abs(z)))`, which is not a p-value for any hypothesis. The two expressions differ in where they put the threshold: the deposit's calls a difference significant at the 0.05 level once `|z|` exceeds 1.82, where the two-tailed test needs 1.96. Of the 21 characteristics in appendix Table 1, extraversion is the only one whose verdict falls between the two, and the corrections below are what follows for the two sentences that count significant differences. The standard errors themselves come from an unseeded bootstrap and are not exactly reproducible, so both corrections are recomputed from the distance and the standard error appendix Table 1 prints, which do not move; the maintained rewrite's own run agrees with each.

```{r rendered-entries, results="asis"}
walk(entries$entry, emit)
```

```{r emit-spine}
# The machine-readable spine, written wherever this document is rendered. Anything else
# that needs these entries reads it rather than keeping its own copy, so the two cannot
# drift.
write_csv(entries, here("errata_entries.csv"))
```
